---
title: "Reproducible Analytical Pipelines - Example report"
format: html
editor: visual
---

```{r}
#| echo: false

# Set the working directory location
setwd('~/OneDrive - Warren House Group/DSDL/Projects/Think Forward/capacity_development/raps_and_tools/')

# Read in the raw data in CSV format
data <- read.csv('data/report1_transform.csv')

data$Amount <- as.numeric(data$Amount)
data$Total.Price <- as.numeric(data$Total.Price)
options(scipen = 5)
tot_amount <- sum(data$Amount)
tot_price <- sum(data$Total.Price)

```

## Test report

### In-text numbers

Out total amount of product produced is `r tot_amount` units at a price of £`r tot_price`.

### Adding a table

```{r}
#| echo: false
#| label: tbl-negot
#| tbl-cap: "Negotiation details"

library(knitr)
negot_sub <- data[data$Stage == "Negotiation", ]
negot_tab <- negot_sub[c("Account.Name", "project_length", "Amount", "Total.Price")]

kable(negot_tab, col.names = c("Customer", "Project length (days)", "Quantity", "Price (GBP)"), row.names = FALSE)
```

The information on our current contracts at the negotiation stage are shown in @tbl-negot.

### Adding a plot

```{r}
#| echo: false
#| label: fig-bar
#| fig-cap: "Bar chart of the number of projects by customer"

acc_count <- table(data$Account.Name)
max_count <- which.max(acc_count)
cust_plt <- barplot(acc_count)
```

The number of projects for each customer are shown in @fig-bar. The customer with the greatest number of projects is `r names(max_count)`. We currently have `r acc_count[[max_count]]` projects with them.

```{r}
#| echo: false
#| label: fig-scatter
#| fig-cap: "A scatter plot comparing the length of a project and the price of the project"

price_amount_plt <- plot(data$project_length, data$Total.Price,
                         xlab = "Project length (days)",
                         ylab = "Total price (GBP)")

avg_len <- mean(data$project_length)
std_len <- round(sd(data$project_length), 2)
```

The relationship between the length of a project and the price of the project is given in @fig-scatter. The average project length is `r avg_len` (standard deviation = `r std_len`) and the average project price is `r mean(data$Total.Price)` (standard deviation = `r round(sd(data$project_length),2)`).


